---
title: "HuYuDataInsight LLC"
author: "Zhaowei Cai"
date: "2024-05-02"
output:
  pdf_document: default
  html_document: default
---


# Loading packages
```{r}
library(tseries)
library(forecast)
library(stringr)
library(PerformanceAnalytics)
library(xts)
```

# Question 1
```{r}
set.seed(123)
#create a time series with right observations and first element is 0
ts_sim <- arima.sim(list(order = c(1,0,1), ar=0.5, ma=0.4), n = 410) + 3

left <- 401
right <- 410
it <- left:right
```


```{r}
plot(ts_sim, col=4, las=1)
abline(v=c(1, left, right), lty="dotted", col=4)
```

# Question 2


```{r}
myts = subset(ts_sim, subset=rep(c(TRUE, FALSE), times=c(400, 10)))
```

## Step 1: visualize myts
```{r}
plot.zoo(myts, col=4, las=1, main="Time Series")
```
## Step 2: unit root test (augmented Dickey-Fuller) of myts
```{r}
adf.test(myts, alternative = 'stationary')
kpss.test(myts)
```
We have used both the KPSS test and the ADF Unit root test to check the stationary. The null hypothesis of the Unit root test (Adf.test) is rejected while the null hypothesis of KPSS test is accepted.
Both indicate the data are stationary.

## Step 3: Identifying lags
```{r}
acf(myts)
pacf(myts)
```
The Partial ACF cut off after first lag, it shows the MA(1) part of ARIMA model (q=1).

## Step 4: train the model with auto.arima
```{r}
fit_myts = auto.arima(
  myts,
  max.p = 3,
  max.q = 3,
  ic = "aicc",
  seasonal = FALSE,
  stationary = TRUE,
  lambda = NULL,
  stepwise = FALSE,
  approximation = FALSE,
  trace = T
)
best.fit = arima(myts, c(1,0,1))
summary(best.fit)
```
There is an intercept equal to 3.0225.

```{r}
checkresiduals(best.fit)
Box.test(best.fit$residuals)
```
The p-value is higher than 0.05, so there is little evidence of non-zero autocorrelations in the forecast errors.

```{r}
shapiro.test(best.fit$residuals)
```
Shapiro-Wilk test confirms the normally distributed residuals as well.


# Question 3

```{r}
forecast_myts = forecast(fit_myts, h=10, level=0.95)
plot(forecast_myts, col=4, las=1)
abline(v=c(1, 400, 410), lty="dotted", col=4)
lines(401:410, ts_sim[401:410], lty="dotted", col="red")
# red is observation and blue is prediction
```

```{r}
# since it is one step ahead predictin, so we need use for loop
pred_df <- data.frame(NULL)
for(t in 401:410){
  pred_onestep <- forecast(ts_sim[1:t], h=1, level=0.95, model = fit_myts)
  pred_df <- rbind(pred_df, data.frame(mean = pred_onestep$mean[1], lower = pred_onestep$lower[1], upper = pred_onestep$upper[1]))
}
```

```{r}
plot(ts_sim, col=4, las=1)
abline(v=c(1, left, right), lty="dotted", col=4)

lines(it, pred_df$mean, col = 'red')
lines(it, pred_df$lower, col = 'green')
lines(it, pred_df$upper, col = 'green')
legend(40, 40, legend=c("Observations", "Prediction", "Bounds of CI"),col=c("blue", "red", "green"),lty = 1, cex=0.8)
```


# Question 4

```{r}
#(a)
data = read.csv('TSLA1.csv')

library(forecast)
library(zoo)
library(tseries)
TSLA = data$Close
time = as.Date(data$Date, format = '%m/%d/%y')
df = data.frame(datefield = time, TSLA = TSLA)
TSLA_stock = with(df, zoo(TSLA, order.by = time))
plot.zoo(TSLA_stock, col=4, las=1, main="TSLA")

# Use the closing price to get log return
log_return = na.omit(diff(log(data$Close))) # log return
time = as.Date(data$Date, format = '%m/%d/%y')[-1]
df = data.frame(datefield = time, TSLA = log_return)
TSLA_return = with(df, zoo(TSLA, order.by = time))
plot(df, main = "TSLA log returns")
plot.zoo(TSLA_return, col=4, las=1, main="TSLA")

adf.test(log_return)
kpss.test(log_return)
# Stationary
acf(log_return)
pacf(log_return)

model <- auto.arima(log_return, trace = T)
model

checkresiduals(model)
Box.test(model$residuals)
shapiro.test(model$residuals)

# (b)
# Log return is the first order diff of logged closing price.
log_cp = log(data$Close)
model <- auto.arima(log_cp, trace = T)
# ARIMA(0,1,0)
```